Draft_Application_Stochastic_Volatility

### 2021-07-15 Real Dataset SV.Rmd
changes
a

As regards the series that we will employ in section (\textit{fill with the number of the section}), namely the series of realised volatilities which we will employ as a proxy for the true latent volatilities, the data were retrieved from the Oxford-Man Institute's Realized Library, which provides several different daily non-parametric measures of past volatility. We considered a proper rescaling of the \textit{rv5} series, \textit{i.e.} model-free daily volatility estimated based on 5 min intraday return intervals. Also in this case, the chosen interval spanned from June 1st, 2017 to May 30th, 2021.

@@

Heber, Gerd, Asger Lunde, Neil Shephard and Kevin Sheppard (2009). Oxford-Man Institute's realized library. Oxford-Man Institute, University of Oxford, version 0.3. Available from: https://realized.oxford-man.ox.ac.uk/. \

>>>>

As regards the series that we will employ in section (\textit{fill with the number of the section}), namely the series of realised volatilities which we will employ as a proxy for the true latent volatilities, the data were retrieved from the Oxford-Man Institute's Realized Library, which provides several different daily non-parametric measures of past volatility. We consider a proper rescaling of the \textit{rv5} series, \textit{i.e.} model-free daily volatility estimates based on 5 min intraday return intervals. Also in this case, the chosen interval spanned from June 1st, 2017 to May 30th, 2021.

@@

Heber, Gerd, Asger Lunde, Neil Shephard and Kevin Sheppard (2009). Oxford-Man Institute's realized library. Oxford-Man Institute, University of Oxford, version 0.3. Available at: https://realized.oxford-man.ox.ac.uk/. \
